### 2017-03-20 thesis/methods/methods.tex
Finished editing results1

The raw Affymetrix HGU133A microarray gene expression data files from the \citet{Print2016} study were downloaded from the \gls{geo} database (\gls{geo} accession ID: GSE3\-6771).
Clinical data for the samples (age, ethnicity, tumour grade, breast cancer subtype, \gls{er}/\gls{pr} statuses, \gls{ln} status, \gls{bmi} and treatments used) in this study was obtained from Professor Cris Print (personal communication with Assoc. Prof. Mik Black).

@@

	\begin{longtable}{lcc}
		\caption{Summary of the clinical variables in the Creighton \textit{et al.} and \gls{nzbc} microarray data}
		\label{tab:clin_summary}\\
		Clinical variable & Creighton \textit{et al.} & \gls{nzbc} \\
		\endfirsthead
		\multicolumn{3}{c}{\tablename\ \thetable{}\ (continued)}\\
		\endhead
		\hline
		\hline
		\rule{0pt}{2.25ex}Age \\
		\hspace{1em} Min.                    & 30 & 31 \\
		\hspace{1em} Max.                    & 72 & 92 \\
		\hspace{1em} Mean                    & 49 & 59 \\
		\hspace{1em} Median                  & 48 & 60 \\
		\hline
		\rule{0pt}{2.25ex}Ethnicity         \\
		\hspace{1em} Caucasian               & 77 & 71 \\
		\hspace{1em} African-American        & 16 & 0  \\
		\hspace{1em} \gls{nz} M\=aori        & 0  & 10 \\
		\hspace{1em} Pacific Islands         & 0  & 14 \\
		\hspace{1em} Asian                   & 10 & 4  \\
		\hline
		\rule{0pt}{2.25ex}\gls{bmi} status  \\
		\hspace{1em} Normal weight           & 36 & 28 \\
		\hspace{1em} Overweight              & 29 & 28 \\
		\hspace{1em} Obese                   & 38 & 43 \\
		\hline
		\rule{0pt}{2.25ex}Menopause status  \\
		\hspace{1em} Premenopause            & 49 & NA\tnote{1}\\
		\hspace{1em} Perimenopause           & 9  & NA \\
		\hspace{1em} Postmenopause           & 45 & NA \\
		\hline
		\rule{0pt}{2.25ex}Tumour grade      \\
		\hspace{1em} 1                       & 14 & 11 \\
		\hspace{1em} 2                       & 35 & 39 \\
		\hspace{1em} 3                       & 54 & 49 \\
		\hline
		\rule{0pt}{2.25ex}\gls{er} status   \\
		\hspace{1em} \gls{er}$^+$            & 58 & 72 \\
		\hspace{1em} \gls{er}$^-$            & 42 & 27 \\
		\hspace{1em} Unknown                 & 3  & 0  \\
		\hline
		\rule{0pt}{2.25ex}\gls{pr} status   \\
		\hspace{1em} \gls{pr}$^+$            & 48 & 62 \\
		\hspace{1em} \gls{pr}$^-$            & 50 & 37 \\
		\hspace{1em} Unknown                 & 5  & 0  \\
		\hline
		\rule{0pt}{2.25ex}\gls{her2} status \\
		\hspace{1em} \gls{her2}$^+$          & 12 & NA \\
		\hspace{1em} \gls{her2}$^-$          & 54 & NA \\
		\hspace{1em} Unknown                 & 37 & NA \\
		\hline
		\rule{0pt}{2.25ex}\gls{ln} status   \\
		\hspace{1em} \gls{ln}$^+$            & 14 & 56\\
		\hspace{1em} \gls{ln}$^-$            & 89 & 40\\
		\hspace{1em} Unknown                 & 0  & 3 \\
		\hline
		\hline
		\hspace{12em}\insertTableNotes
	\end{longtable}
\end{ThreePartTable}

@@

To overcome this limitation, \citet{Law2014} developed a method called ``variance modelling at the observational level'', or ``voom'', that allows any \gls{rnaseq} data to be used in any existing statistical analysis pipeline that is precision weight aware, including pipelines used for microarray data analyses.
% TODO: check the meaning of precision weight in the above sentence
In brief, voom first constructs a standard deviation trend from the logged \gls{cpm} value of the genes (experimental design, treatment conditions and other factors are taken into account).
This trend is then used to interpolate the standard deviation of the observation based on its predicted count size, and the inverse square of the predicted standard deviation is used as the weight  for that observation.
The weights of the observations and the logged \gls{cpm} can then be used in other statistical pipelines that allow the input of quantitative weights \citep{Law2014}.

@@

The summary statistics from the \texttt{eBayes} function can be displayed with the \texttt{topTable} function (\textit{limma}) and includes the estimate of the fold change of the gene expression in log$_2$, average gene expression level in log$_2$, moderated \textit{t}-statistic, raw p-value of the gene, multiple hypothesis testing adjusted p-value, and \textit{B}-statistic.
The first value shows the estimate of the log$_2$ fold change of the gene expression compared with the reference group, so this represents the log$_2$ fold change of the gene expression in the obese samples relative to the non-obese group.
The second value presents the log$_2$ value of the average expression of the gene across all of the arrays/samples.
%TODO: more details on simple Bayesian method
The moderated \textit{t}-statistic is the same as normal \textit{t}-statistic, but its standard error has been adjusted by a simple Bayesian method \citep{Smyth2005}.
Raw p-value and adjusted p-value represent the p-value of the gene before and after it has been corrected for multiple hypothesis testing, respectively.
Lastly, the value of \textit{B}-statistic represents the log-odds that the gene is differentially expressed, where \textit{B}-statistic of 0 shows that there is a 50\% chance the gene is differentially expressed \citep{Smyth2005}.

@@

\begin{longtable}{llp{8cm}}
	\caption{18 pathways from \citet{Gatza2010a} and its respective genes used to check the direction of the pathway metagene}
	\label{tab:metagene_direction}\\
	\centering
	Pathway & Representative gene & Brief pathway description\\
	\hline
	\hline
	\endfirsthead
	\multicolumn{3}{c}{\tablename\ \thetable{}\ (continued)}\\
	\hline
	\hline
	\endhead
	\hline
	\hline
	\endlastfoot
	\rule{0pt}{2.25ex}Akt         & AKT1   & Also known as protein kinase B; involved in cell survival\\
	\rule{0pt}{2.25ex}\gls{bcat}  & CTNNB1 & $\beta$-catenin; involved in the Wnt signalling pathway and cell-cell adhesion\\
	\rule{0pt}{2.25ex}E2F1        & E2F1   & Member of the E2F transcription factor family in higher eukaryotes; involved in cell cycle regulation\\
	\rule{0pt}{2.25ex}\Gls{egfr}  & EGFR   & Also known as ERBB1 or HER1; involved in signalling the pathways for cell proliferation \\
	\rule{0pt}{2.25ex}\Gls{er}    & ESR1   & Involved in cell cycle regulation, cell proliferation and cell survival\\
	\rule{0pt}{2.25ex}\Gls{her2}  & ERBB2  & Also known as ERBB2; involved in cell proliferaion and apoptosis\\
	\rule{0pt}{2.25ex}\Gls{ifna}  & IFNA1  & Cytokine involved in innate immune response against viral infection\\
	\rule{0pt}{2.25ex}\Gls{ifny}  & IFNG   & Cytokine critical for innate and adaptive immune response\\
	\rule{0pt}{2.25ex}Myc         & MYC    & Transcription factor involved in cell proliferaion, cell growth and apoptosis\\
	\rule{0pt}{2.25ex}p53         & TP53   & Tumour suppressor protein involved in \acrshort{dna} repair, cell cycle regulation and apoptosis\\
	\rule{0pt}{2.25ex}p63         & TP63   & Involved in development\\
	\rule{0pt}{2.25ex}\Gls{pi3k}  & PIK3CA & Involved in cell growth, cell proliferaion, cell differentiation and cell survival\\
	\rule{0pt}{2.25ex}\Gls{pr}    & PGR    & Signal transducer that activates other signalling pathways; involved in cell proliferation\\
	\rule{0pt}{2.25ex}Ras         & HRAS   & Involved in cell proliferaion, cell differentiation, cell adhesion, apoptosis and cell migration\\
	\rule{0pt}{2.25ex}\Gls{stat3} & STAT3  & Involved in cell growth and apoptosis\\
	\rule{0pt}{2.25ex}Src         & SRC    & Involved in cell survival, angiogenesis, cell proliferation and cell invasion\\
	\rule{0pt}{2.25ex}\Gls{tgfb}  & TGFB1  & Involved in cell proliferation, cell differentiation and apoptosis\\
	\rule{0pt}{2.25ex}\Gls{tnfa}  & TNF    & Involved in immune response, inflammation and apoptosis\\
\end{longtable}

@@

%TODO: re-write the linear model stuff:

>>>>

To provide an insight into the relevance of the obesity associated genetic signatures in \gls{nz} patient cohort, the \gls{nzbc} data set used by \citet{Print2016} were used.
The raw Affymetrix HGU133A microarray gene expression data files from the \citet{Print2016} study were downloaded from the \gls{geo} database (\gls{geo} accession ID: GSE3\-6771).
Clinical data for the samples (age, ethnicity, tumour grade, breast cancer subtype, \gls{er}/\gls{pr} statuses, \gls{ln} status, \gls{bmi} and treatments used) in this study was obtained from Prof. Cris Print (personal communication with Assoc. Prof. Mik Black).

@@

	\newpage
	\begin{longtable}{lcc}
		\caption{Summary of the clinical variables in the Creighton \textit{et al.} and \gls{nzbc} microarray data}
		\label{tab:clin_summary}\\
		Clinical variable & Creighton \textit{et al.} & \gls{nzbc} \\
		\endfirsthead
		\multicolumn{3}{c}{\tablename\ \thetable{}\ (continued)}\\
		\endhead
		\hline
		\hline
		\rule{0pt}{2.25ex}Age \\
		\hspace{1em} Min.                    & 30 & 31 \\
		\hspace{1em} Max.                    & 72 & 92 \\
		\hspace{1em} Mean                    & 49 & 59 \\
		\hspace{1em} Median                  & 48 & 60 \\
		\hline
		\rule{0pt}{2.25ex}Ethnicity         \\
		\hspace{1em} Caucasian               & 77 & 71 \\
		\hspace{1em} African-American        & 16 & 0  \\
		\hspace{1em} \gls{nz} M\=aori        & 0  & 10 \\
		\hspace{1em} Pacific Islands         & 0  & 14 \\
		\hspace{1em} Asian                   & 10 & 4  \\
		\hline
		\rule{0pt}{2.25ex}\gls{bmi} status  \\
		\hspace{1em} Normal weight           & 36 & 28 \\
		\hspace{1em} Overweight              & 29 & 28 \\
		\hspace{1em} Obese                   & 38 & 43 \\
		\hline
		\rule{0pt}{2.25ex}Menopause status  \\
		\hspace{1em} Premenopause            & 49 & NA\tnote{1}\\
		\hspace{1em} Perimenopause           & 9  & NA \\
		\hspace{1em} Postmenopause           & 45 & NA \\
		\hline
		\rule{0pt}{2.25ex}Tumour grade      \\
		\hspace{1em} 1                       & 14 & 11 \\
		\hspace{1em} 2                       & 35 & 39 \\
		\hspace{1em} 3                       & 54 & 49 \\
		\hline
		\rule{0pt}{2.25ex}\gls{er} status   \\
		\hspace{1em} \gls{er}$^+$            & 58 & 72 \\
		\hspace{1em} \gls{er}$^-$            & 42 & 27 \\
		\hspace{1em} Unknown                 & 3  & 0  \\
		\hline
		\rule{0pt}{2.25ex}\gls{pr} status   \\
		\hspace{1em} \gls{pr}$^+$            & 48 & 62 \\
		\hspace{1em} \gls{pr}$^-$            & 50 & 37 \\
		\hspace{1em} Unknown                 & 5  & 0  \\
		\hline
		\rule{0pt}{2.25ex}\gls{her2} status \\
		\hspace{1em} \gls{her2}$^+$          & 12 & NA \\
		\hspace{1em} \gls{her2}$^-$          & 54 & NA \\
		\hspace{1em} Unknown                 & 37 & NA \\
		\hline
		\rule{0pt}{2.25ex}\gls{ln} status   \\
		\hspace{1em} \gls{ln}$^+$            & 14 & 56\\
		\hspace{1em} \gls{ln}$^-$            & 89 & 40\\
		\hspace{1em} Unknown                 & 0  & 3 \\
		\hline
		\hline
		\insertTableNotes
	\end{longtable}
\end{ThreePartTable}

@@

To overcome this limitation, \citet{Law2014} developed a method called ``variance modelling at the observational level'', or ``voom'', that allows any \gls{rnaseq} data to be used in ``any statistical pipeline for microarray data that is precision weight aware''.
In brief, voom first constructs a standard deviation trend from the logged \gls{cpm} value of the genes (experimental design, treatment conditions and other factors are taken into account).
This trend is then used to interpolate the standard deviation of the observation based on its predicted count size, and the inverse square of the predicted standard deviation is used as the weight  for that observation.
The weights of the observations and the logged \gls{cpm} can then be used in other statistical pipelines that allow the input of quantitative weights \citep{Law2014}.

@@

The summary statistics from the \texttt{eBayes} function can be displayed with the \texttt{topTable} function (\textit{limma}) and includes the estimate of the fold change of the gene expression in log$_2$, average gene expression level in log$_2$, moderated \textit{t}-statistic, raw p-value of the gene, multiple hypothesis testing adjusted p-value, and \textit{B}-statistic.
The first value shows the estimate of the log$_2$ fold change of the gene expression compared with the reference group, so this represents the log$_2$ fold change of the gene expression in the obese samples relative to the non-obese group.
The second value presents the log$_2$ value of the average expression of the gene across all of the arrays/samples.
The moderated \textit{t}-statistic is the same as normal \textit{t}-statistic, but its standard error has been adjusted (or ``shrunk'') toward a common value by a simple Bayesian method \citep{Smyth2005}.
Raw p-value and adjusted p-value represent the p-value of the gene before and after it has been corrected for multiple hypothesis testing, respectively.
Lastly, the value of \textit{B}-statistic represents the log-odds that the gene is differentially expressed, where \textit{B}-statistic of 0 shows that there is a 50\% chance the gene is differentially expressed \citep{Smyth2005}.

@@

\begin{longtable}{llp{8cm}}
	\caption{18 pathways from \citet{Gatza2010a} and its respective genes used to check the direction of the pathway metagene}
	\label{tab:metagene_direction}\\
	\centering
	Pathway & Representative gene & Brief pathway description\\
	\hline
	\hline
	\endfirsthead
	\multicolumn{3}{c}{\tablename\ \thetable{}\ (continued)}\\
	\hline
	\hline
	\endhead
	\hline
	\hline
	\endlastfoot
	\rule{0pt}{2.25ex}Akt         & AKT1   & Also known as protein kinase B; involved in cell survival\\
	\hline
	\rule{0pt}{2.25ex}\gls{bcat}  & CTNNB1 & $\beta$-catenin; involved in the Wnt signalling pathway and cell-cell adhesion\\
	\hline
	\rule{0pt}{2.25ex}E2F1        & E2F1   & Member of the E2F transcription factor family in higher eukaryotes; involved in cell cycle regulation\\
	\hline
	\rule{0pt}{2.25ex}\Gls{egfr}  & EGFR   & Also known as ERBB1 or HER1; involved in signalling the pathways for cell proliferation \\
	\hline
	\rule{0pt}{2.25ex}\Gls{er}    & ESR1   & Involved in cell cycle regulation, cell proliferation and cell survival\\
	\hline
	\rule{0pt}{2.25ex}\Gls{her2}  & ERBB2  & Also known as ERBB2; involved in cell proliferaion and apoptosis\\
	\hline
	\rule{0pt}{2.25ex}\Gls{ifna}  & IFNA1  & Cytokine involved in innate immune response against viral infection\\
	\hline
	\rule{0pt}{2.25ex}\Gls{ifny}  & IFNG   & Cytokine critical for innate and adaptive immune response\\
	\hline
	\rule{0pt}{2.25ex}Myc         & MYC    & Transcription factor involved in cell proliferaion, cell growth and apoptosis\\
	\hline
	\rule{0pt}{2.25ex}p53         & TP53   & Tumour suppressor protein involved in \acrshort{dna} repair, cell cycle regulation and apoptosis\\
	\hline
	\rule{0pt}{2.25ex}p63         & TP63   & Involved in development\\
	\hline
	\rule{0pt}{2.25ex}\Gls{pi3k}  & PIK3CA & Involved in cell growth, cell proliferaion, cell differentiation and cell survival\\
	\hline
	\rule{0pt}{2.25ex}\Gls{pr}    & PGR    & Signal transducer that activates other signalling pathways; involved in cell proliferation\\
	\hline
	\rule{0pt}{2.25ex}Ras         & HRAS   & Involved in cell proliferaion, cell differentiation, cell adhesion, apoptosis and cell migration\\
	\hline
	\rule{0pt}{2.25ex}\Gls{stat3} & STAT3  & Involved in cell growth and apoptosis\\
	\hline
	\rule{0pt}{2.25ex}Src         & SRC    & Involved in cell survival, angiogenesis, cell proliferation and cell invasion\\
	\hline
	\rule{0pt}{2.25ex}\Gls{tgfb}  & TGFB1  & Involved in cell proliferation, cell differentiation and apoptosis\\
	\hline
	\rule{0pt}{2.25ex}\Gls{tnfa}  & TNF    & Involved in immune response, inflammation and apoptosis\\
\end{longtable}

@@

### 2017-03-20 thesis/misc/appendix.tex
Finished editing results1

@@

%TODO: add FM metagene plots for ICGC

>>>>

	\cref{fig:appendix/fm_ob_meta_heatmap_icgc} shows the association of the FM obesity metagene with the gene expression pattern of the FM obesity associated genetic signature in the other \gls{icgc} cancer data sets.
	\cref{fig:appendix/fm_ob_meta_box_scatter_icgc} shows the association of the FM obesity metagene scores with the patient \gls{bmi} and \gls{bmi} status.
	Clearly, the FM metagene was able to capture the overall gene expression patterns, but was not significantly associated with the patient \gls{bmi} or \gls{bmi} status.

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/fm_meta_ICGC}\\
		\includegraphics[width=0.32\linewidth,page=13]{appendix/fm_meta_ICGC}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/fm_meta_ICGC}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/fm_meta_ICGC}\\
		\includegraphics[width=0.32\linewidth,page=28]{appendix/fm_meta_ICGC}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/fm_meta_ICGC}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/fm_meta_ICGC}\\
		\caption[Association of the FM obesity metagene with the sample gene expressions in the other \gls{icgc} data]{Heatmaps showing the association of the FM obesity metagenes  with the sample gene expressions in the other \gls{icgc} data sets.
		Scales are as described in previous figures.}
		\label{fig:appendix/fm_ob_meta_heatmap_icgc}
	\end{figure}

	\begin{figure}[htpb]
		\centering
		\includegraphics[page=9,width=0.42\linewidth]{appendix/fm_meta_ICGC}
		\hfill
		\includegraphics[page=10,width=0.42\linewidth]{appendix/fm_meta_ICGC}\\
		\caption[Association of the FM obesity metagene with the patient \gls{bmi}/\gls{bmi} status in the other \gls{icgc} data]{Box plots and scatter plots showing the association of the FM obesity metagene with the patient \gls{bmi} status  and \gls{bmi}, respectively, in the \gls{icgc} data sets.
		P-values and $R^2$-value are as described in previous figures.}
		\label{fig:appendix/fm_ob_meta_box_scatter_icgc}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=14,width=0.45\linewidth]{appendix/fm_meta_ICGC}
		\hfill
		\includegraphics[page=15,width=0.45\linewidth]{appendix/fm_meta_ICGC}\\
		\includegraphics[page=19,width=0.45\linewidth]{appendix/fm_meta_ICGC}
		\hfill
		\includegraphics[page=20,width=0.45\linewidth]{appendix/fm_meta_ICGC}\\
		\includegraphics[page=24,width=0.45\linewidth]{appendix/fm_meta_ICGC}
		\hfill
		\includegraphics[page=25,width=0.45\linewidth]{appendix/fm_meta_ICGC}\\
		\caption{Name}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=29,width=0.45\linewidth]{appendix/fm_meta_ICGC}
		\hfill
		\includegraphics[page=30,width=0.45\linewidth]{appendix/fm_meta_ICGC}\\
		\includegraphics[page=34,width=0.45\linewidth]{appendix/fm_meta_ICGC}
		\hfill
		\includegraphics[page=35,width=0.45\linewidth]{appendix/fm_meta_ICGC}\\
		\includegraphics[page=39,width=0.45\linewidth]{appendix/fm_meta_ICGC}
		\hfill
		\includegraphics[page=40,width=0.45\linewidth]{appendix/fm_meta_ICGC}\\
		\caption{Name}
	\end{figure}

	\section{Direction of all the obesity metagenes from the CR data}
	\label{sec:direction_of_all_the_obesity_metagenes_from_the_cr_data}

	The direction of the obesity metagenes identified from the CR data were examined and corrected for (\cref{fig:crob_meta_direction}).
	Gene probes that were common to all obesity associated genetic signatures were used to examine whether the metagene was in the correct direction, relative to the other obesity metagenes

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.32\linewidth,page=3]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/cr_meta_direction_raw}\\
		\includegraphics[width=0.32\linewidth,page=9]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=15]{appendix/cr_meta_direction_raw}\\
		\includegraphics[width=0.32\linewidth,page=18]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=21]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=24]{appendix/cr_meta_direction_raw}\\
		\caption[Directionality of the obesity metagenes in the CR data]{Heatmaps showing the gene expression of the obesity associated genetic signatures with the obesity metagene in \gls{rma}-normalised CR data set.
		The gene probes that were common to all of the obesity associated genetic signatures were used to determine the direction of the obesity metagenes.
		The scales and axes are the same as the previous heatmaps.
		}
		\label{fig:crob_meta_direction}
	\end{figure}

@@

	\section{Obesity associated genetic signature using sample \gls{bmi} values}
	\label{sec:obesity_associated_genetic_signature_using_sample_bmi_values}

	Since all of these obesity associated genetic signatures were derived based on the discrete values of sample \gls{bmi} staus, a genetic signature was identified using the sample \gls{bmi} value (continuous variable).
	Gene probe expressions were correlated with the sample \gls{bmi} values and was corrected for multiple hypothesis testing with \gls{fdr}.
	There were no significant gene that correlated with the sample \gls{bmi} (p \textless{} 0.05).

	With that said, the top 799 gene probes that correlated the most with the sample \gls{bmi} were examined to see if there was any association.
	The results were similar to the other obesity associated genetic signatures: the continuous \gls{bmi} signature significantly associated with sample \gls{bmi} and \gls{bmi} status in the CR data, but did not show any significance in any of the other cancer data.

	\begin{figure}[htp!]
		\centering
		\includegraphics[page=3,width=0.8\linewidth]{appendix/contbmi_cr}\\
		\includegraphics[page=4,width=0.45\linewidth]{appendix/contbmi_cr}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/contbmi_cr}
		\caption[Continuous \gls{bmi} metagene in various cancer data]{Heatmap, box plot and scatter plot showing the association of the continuous \gls{bmi} metagene with the sample gene expression, \gls{bmi} and \gls{bmi} status, respectively, in various cancer data.
		Scales, p-values and $R^2$-value are as described in previous figures.}
		\label{fig:cont_bmi}
	\end{figure}

	\begin{figure}[htp!]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=3,width=0.8\linewidth]{appendix/contbmi_ICGC}\\
		\includegraphics[page=4,width=0.45\linewidth]{appendix/contbmi_ICGC}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/contbmi_ICGC}
		\caption{hello}
	\end{figure}

	\begin{figure}[htp!]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[page=3,width=0.8\linewidth]{appendix/contbmi_cris}\\
		\includegraphics[page=4,width=0.45\linewidth]{appendix/contbmi_cris}
		\hfill
		\includegraphics[page=5,width=0.45\linewidth]{appendix/contbmi_cris}
		\caption{hello}
	\end{figure}

\section{Pathways significant in each of the cancer types}
\label{sec:pathways_significant_in_each_of_the_cancer_types}

\begin{table}[htpb]
	\centering
	\caption{Significantly enriched \gls{kegg} pathways in \gls{icgc} cancer data}
	\label{tab:sig_path_kegg}
	\begin{threeparttable}
		\begin{tabular}{ll}
			Cancer type                      & Pathway         \\
			\hline
			\hline
				\rule{0pt}{2.25ex}\gls{blca} & NA\tnote{1}             \\
				\gls{cesc}                   & ABC transporter \\
				\gls{coad}                   & NA              \\
				\gls{kirp}                   & NA              \\
				\gls{lihc}                   & NA              \\
				\gls{read}                   & NA              \\
				\gls{skcm}                   & NA              \\
				\gls{ucec}                   & NA              \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] Not available (no pathway enriched)
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\begin{table}[htpb]
	\centering
	\caption{Significantly enriched Reactome pathways in \gls{icgc} cancer data}
	\label{tab:sig_path_reactome}
	\begin{threeparttable}
		\begin{tabular}{ll}
			Cancer type & Pathway \\
			\hline
			\hline
				\rule{0pt}{2.25ex}\gls{blca} & Phosphate bond hydrolysis by NUDT proteins \\
				\gls{cesc}                   & Mitochondrial ABC transporters             \\
				\gls{coad}   & NA\tnote{1}               \\
				\gls{kirp}   & NA             \\
				\gls{lihc}   & NA             \\
				\gls{read}   & NA             \\
				\gls{skcm}   & NA             \\
				\gls{ucec}   & NA             \\
			\hline
			\hline
		\end{tabular}
		\begin{tablenotes}
			\item [1] Not available (no pathway enriched)
		\end{tablenotes}
	\end{threeparttable}
\end{table}

\newpage

	\begin{TableNotes}
		\begin{footnotesize}
			\item [1] Not available (no pathway enriched)
		\end{footnotesize}
	\end{TableNotes}

\begin{longtable}{lp{0.8\textwidth}}
	\centering
	\label{tab:sig_path_go}\\
	Cancer type & Pathway\\
	\endfirsthead
	\multicolumn{2}{c}{\tablename\ \thetable{}\ (continued)} \\
	\hline
	\hline
	\endhead
	\hline
	\hline
	\rule{0pt}{2.25ex}\gls{blca} & Nucleobase-containing small molecule catabolic process                                          \\
                                 & SUMO-specific protease activity                                                                 \\
                                 & Diphosphoinositol-polyphosphate diphosphatase activity                                          \\
                                 & Inositol diphosphate tetrakisphosphate diphosphatase activity                                   \\
                                 & Inositol-1-diphosphate-2,3,4,5,6-pentakisphosphate diphosphatase activity                       \\
                                 & Inositol-3-diphosphate-1,2,4,5,6-pentakisphosphate diphosphatase activity                       \\
                                 & Inositol-5-diphosphate-1,2,3,4,6-pentakisphosphate diphosphatase activity                       \\
                                 & Inositol-1,5-bisdiphosphate-2,3,4,6-tetrakisphosphate 1-diphosphatase activity                  \\
                                 & Inositol-1,5-bisdiphosphate-2,3,4,6-tetrakisphosphate 5-diphosphatase activity                  \\
                                 & Inositol-3,5-bisdiphosphate-2,3,4,6-tetrakisphosphate 5-diphosphatase activity                  \\
                                 & Phosphatidylinositol 3-kinase complex, class IB                                                 \\
                                 & Neurotrophin binding                                                                            \\
                                 & 1-phosphatidylinositol-5-phosphate 4-kinase activity                                            \\
                                 & Coagulation                                                                                     \\
                                 & Cholesterol O-acyltransferase activity                                                          \\
                                 & Pyrimidine deoxyribonucleotide catabolic process                                                \\
                                 & Nucleotidase activity                                                                           \\
                                 & G-protein coupled neurotensin receptor activity                                                 \\
                                 & 8-oxo-7,8-dihydroguanosine triphosphate pyrophosphatase activity                                \\
                                 & 8-oxo-7,8-dihydrodeoxyguanosine triphosphate pyrophosphatase activity                           \\
                                 & IDP catabolic process                                                                           \\
                                 & ADP-sugar diphosphatase activity                                                                \\
	\hline
	\gls{cesc}                   & ATP-binding cassette (ABC) transporter complex                                                  \\
                                 & Protein delipidation                                                                            \\
                                 & Atg8 ligase activity                                                                            \\
                                 & Cyclin-dependent protein kinase 5 holoenzyme complex                                            \\
                                 & Molybdopterin synthase complex                                                                  \\
                                 & Negative regulation of nodal signaling pathway                                                  \\
                                 & Aspartate-tRNA ligase activity                                                                  \\
                                 & Peroxisomal long-chain fatty acid import                                                        \\
                                 & Sterol-transporting ATPase activity                                                             \\
                                 & Negative regulation of intestinal phytosterol absorption                                        \\
                                 & Negative regulation of intestinal cholesterol absorption                                        \\
                                 & Apolipoprotein A-I receptor activity                                                            \\
                                 & Sulfonylurea receptor activity                                                                  \\
                                 & Atg12 transferase activity                                                                      \\
                                 & Superior olivary nucleus maturation                                                             \\
                                 & Cyclin-dependent protein kinase 5 activator activity                                            \\
                                 & ATPase activity, coupled to transmembrane movement of substances                                \\
	\hline
	\gls{coad}                   & NA\tnote{1}                                                                                     \\
	\hline
	\gls{kirp}                   & Trace-amine receptor activity                                                                   \\
                                 & Regulation of viral release from host cell                                                      \\
                                 & Nuclear import                                                                                  \\
	\hline
	\gls{lihc}                   & NA                                                                                              \\
	\hline
	\gls{read}                   & Nuclear polyadenylation-dependent rRNA catabolic process                                        \\
                                 & Nuclear polyadenylation-dependent tRNA catabolic process                                        \\
                                 & Sodium channel complex                                                                          \\
                                 & U1 snRNA 3'-end processing                                                                      \\
                                 & U5 snRNA 3'-end processing                                                                      \\
                                 & Glucuronosyl-N-acetylglucosaminyl-proteoglycan 4-alpha-N-acetylglucosaminyltransferase activity \\
                                 & Pyrroline-5-carboxylate reductase activity                                                      \\
                                 & Hydroxymethylglutaryl-CoA reductase (NADPH) kinase activity                                     \\
                                 & Acetyl-CoA carboxylase kinase activity                                                          \\
                                 & rRNA modification                                                                               \\
                                 & Rab GDP-dissociation inhibitor activity                                                         \\
                                 & Nuclear retention of pre-mRNA with aberrant 3'-ends at the site of transcription                \\
                                 & Cellular polysaccharide biosynthetic process                                                    \\
                                 & Heparan sulfate N-acetylglucosaminyltransferase activity                                        \\
                                 & N-acetylglucosaminyl-proteoglycan 4-beta-glucuronosyltransferase activity                       \\
                                 & Glucuronyl-galactosyl-proteoglycan 4-alpha-N-acetylglucosaminyltransferase activity             \\
                                 & Regulation of RIG-I signaling pathway                                                           \\
                                 & Regulation of cysteine-type endopeptidase activity                                              \\
                                 & Adenylate cyclase-inhibiting serotonin receptor signaling pathway                               \\
                                 & Peptide-O-fucosyltransferase activity                                                           \\
                                 & Interferon-gamma receptor activity                                                              \\
	\hline
	\gls{skcm}                   & Tissue morphogenesis                                                                            \\
                                 & Beta-1,3-galactosyl-O-glycosyl-glycoprotein beta-1,6-N-acetylglucosaminyltransferase activity   \\
                                 & N-acetyllactosaminide beta-1,6-N-acetylglucosaminyltransferase activity                         \\
                                 & Posterior mesonephric tubule development                                                        \\
                                 & Regulation of stem cell differentiation                                                         \\
                                 & Negative regulation of nodal signaling pathway                                                  \\
                                 & Aspartate-tRNA ligase activity                                                                  \\
                                 & Glutamate-cysteine ligase complex                                                               \\
                                 & Glutamate-cysteine ligase activity                                                              \\
                                 & Rab GDP-dissociation inhibitor activity                                                         \\
	\hline
	\gls{ucec}                   & SUMO-specific protease activity                                                                 \\
                                 & Regulation of dendritic cell cytokine production                                                \\
                                 & Detection of triacyl bacterial lipopeptide                                                      \\
                                 & Cellular response to triacyl bacterial lipopeptide                                              \\
                                 & Toll-like receptor 1-Toll-like receptor 2 protein complex                                       \\
                                 & Detection of diacyl bacterial lipopeptide                                                       \\
                                 & Cellular response to diacyl bacterial lipopeptide                                               \\
                                 & Toll-like receptor 2-Toll-like receptor 6 protein complex                                       \\
                                 & Diacyl lipopeptide binding                                                                      \\
                                 & Coagulation                                                                                     \\
                                 & Polo kinase kinase activity                                                                     \\
                                 & Regulation of protein serine/threonine kinase activity                                          \\
                                 & DNA-dependent protein kinase complex                                                            \\
                                 & Methylosome                                                                                     \\
	\hline
	\hline
	\insertTableNotes
\end{longtable}
